\section{Implementation Details}
This section outlines the engineering decisions made during the development of EduMeter. Every choice is detailed to reflect the team’s commitment to technical excellence and architectural integrity. To ensure a robust codebase, several core design principles were strictly followed, including Don’t Repeat Yourself (\textbf{DRY}), the Single Responsibility Principle (\textbf{SRP}), and the Dependency Inversion Principle (\textbf{DIP}). \\

The implementation phase followed this approach: use cases were first mapped to a domain model, followed by the design of the business logic, ending with the persistent relational database. This design-first methodology ended in the final implementation using the Java programming language.

\subsection{Project Dependencies}
The platform relay on several external technologies to operate properly. The choice of these dependencies has been made following the current industrial standard for each one of the components. Particular attention has also been given to the ease of use and maintainability.

\begin{itemize}
	\item \textbf{Maven}: used as build and management tool for the project. 
	\item \textbf{Jakarta RESTful Web Services (JAX-RS)}: employed as the project's RESTful API specification.
	\begin{itemize}
		\item \textbf{JAX-RS}: it's the section of Jakarta EE about RESTful services.
		\item \textbf{Jersey}: implements JAX-RS, specifically utilizing the jersey-container-servlet module.
		\item \textbf{Jackson}: handles the serialization and deserialization of Java objects (POJOs) to JSON format.
		\item \textbf{Glassfish}: a complete application server, which is necessary to export the project as a \textbf{WAR} (Web ARchive), which is runnable by Apache Tomcat.
	\end{itemize}
	\item \textbf{JDBC}: API used for persistent data handling. This allows the Jersey-based backend to perform CRUD operations against the relational database.
	\begin{itemize}
		\item \textbf{PostgreSQL}: concrete implementation of the DB.
	\end{itemize}
	\item \textbf{JUnit Jupiter}: main testing framework. Provides an easy and clear interface to create and run test on the code base.
	\item \textbf{Mockito}: library used with JUnit to isolate components by creating mocks of complex dependencies, such as DAOs.
\end{itemize}

\noindent The project is configured to use Java 17 as the compilation target.

\subsubsection{JAX-RS/Jersey}

JAX-RS/Jersey (from now on referred to as simply "JAX-RS") takes advantage of Java's Annotations and Reflection API. Java Annotations allow to embed meta-data inside types (classes), methods and fields, which can be latered accessed via the Reflection API.


\begin{lstlisting}[language=Java, caption=Example of a Java Annotation being retrievied via the Reflection API.]
@Target(ElementType.FIELD)
@Retention(RetentionPolicy.RUNTIME)
@interface MyCustomAnnotation {}

class Foo {
    @MyCustomAnnotation
    private String bar;
}

void main(String[] args) throws NoSuchFieldException {
    Field barField = Foo.class.getDeclaredField("bar");

    if (barField.isAnnotationPresent(MyCustomAnnotation.class)) {
        // Do something
    }
    else {
        // Do somehting else
    }
}
\end{lstlisting}

JAX-RS leverages these Java features to enable a more quick and idiomatic way of building a RESTful backend. Here's a quick overview of the used JAX-RS annotations and their purpose.

\begin{itemize}
	\item \verb|@Path(String subpath)|: when applied to a method, binds the method to the subpath. The subpath may contain '{varName}', which extracts the path segment to a variable (e.g. \verb|@Path("/user/{userId}")|), see \verb|@PathParam()|. When applied to a class, binds every method of the class to the subpath. If the annotation is present on both the class and the method, binds the method to the concatenation of subpaths.
	\item \verb|@GET/@POST/@PUT/@DELETE|: applies to methods and binds only specific HTTP methods to it.
	\item \verb|@Consums(MediaType type)/@Produces(MediaType type)|: defines what the endpoints accepts and what the endpoints will produce. Can be used as a filter, but it's especially useful to automatically parse and produce JSONs.
	\item \verb|@Inject()|: can be applied to fields and constructors. As object instantiation is often delegated to the framework (e.g. endpoint classses are never explicitly constructed), it becomes a problem when the classes have dependencies that are being passed as constructor argument. In those cases, annotating the constructor with the \verb|Inject()| annotations allows JAX-RS the pass in registered objects as params or to set them as object fields.

	But what are registered objects? During application startup (inside of \texttt{MainApplicaiton.java}), some objects are registered along their type for dependency injection. The fact that objects are registered with their type as their identification, makes it impossibile to register two instance of the same class; this is usually never a problem, as injected dependencies often are or behave like Singletones.

	\item \verb|@Provider|: when applied to classes, makes them discoverable to JAX-RS. In our case, we annotated the exception handlers with \verb|@Provider| to enable them globally.

	\item \verb|@NameBinding|: applies to custom annotations which need later to be applied to \verb|@Provider| classes. These classes are then only available when the custom annotation is present (for example the authentication filter is only applied when the linked annotation is present).

	\item \verb|@QueryParam(String paramName)|: applies to endpoints' arguments. Parses the HTTP requests and sets the value of the argument as the query parameter's value.

	\item \verb|@PathParam(String paramName)|: applies to endpoints' arguments. Parses the HTTP request's subpath and sets the value of the argument as the path parameter extracted with the \verb|@Path()| annotation.

	\item \verb|@HeaderParam(String headerName)|: applies to endpoints' arguments. Parses the HTTP request's headers and sets the value of the argument as the header value of name \verb|headerName|.
\end{itemize}

\subsection{Project Structure}
The project has a standard structure divided into two parts: \verb|main| and \verb|test|. Both the parts got the same directory layout and file's name scheme. This is expecially useful in testing, where package-private field and methods can be accessed by the corresponding test classes, as \verb|main| and \verb|test| are merged together during testing. As highlighted by the directory tree (Figure \ref{fig:tree}), the project is realized following the system architecture described in section \ref{system-architecture-section}. Inside each one of the modules there are the directories containing the packages reported in the overall UML diagram in Figure \ref{UML-overall-diagram}.

\begin{figure}[H]
	\small
	\begin{minipage}{0.8\textwidth}
		\dirtree{%
			.1 src/.
			.2 main/.
			.3 java/.
			.4 com.swe.EduMeter/.
			.5 business\_logic/.
			.6 auth/.
			.7 annotations/.
			.7 filters/.
			.7 CryptoService.java.
			.6 controllers/.
			.6 exception\_handlers/.
			.6 MainApplication.java.
			.5 models/.
			.6 response/.
			.6 ....
			.5 orm/.
			.6 in\_mem\_dao/.
			.6 postgre\_dao/.
			.6 dao/.
			.3 resources/.
			.4 init.sql.
			.2 test/.
			.3 java/.
			.4 com.swe.EduMeter/.
			.5 business\_logic/.
			.6 controllers/.
			.6 ....
			.5 models.
			.6 ....
			.5 orm/.
			.6 ....
		}
	\end{minipage}
	\caption{EduMeter Project Directory Structure}
	\label{fig:tree}
\end{figure}

\subsection{Domain Model}
The domain model is that part of the projects that concerns the entity representation in the code base. Each class in responsible for maintaining its own data consistency and displaying a practical and fast interface to provide the client with a safe and reliable experience. The complete UML class diagram is reported at Figure \ref{UML-domain-model}.

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[scale=0.7, transform shape]
		\begin{umlpackage}{model}
			\umlclass[x=10, type=abstract]{Review}{
				\begin{tabular}{@{} l l @{}}
					-- id & : Integer \\
					-- creatorHash & : String \\
					-- comment & : String \\
					-- date & : LocalDate \\
					-- enjoyment & : int \\
					-- difficulty & : int 
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getters & ... \\
					+ setters & ... 
				\end{tabular}
			}
			
			\umlclass[x=6, y=-7]{DraftedReview}{
				\begin{tabular}{@{} l l @{}}
					-- rawSchool & : String \\
					-- rawDegree & : String \\
					-- rawCourse & : String \\
					-- rawProfessor & : String 
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getters & ... \\
					+ setters & ... 
				\end{tabular}
			}
			
			\umlclass[right=2cm of DraftedReview, y=-7]{PublishedReview}{
				\begin{tabular}{@{} l l @{}}
					-- teachingId &: String \\
					-- upvotedByUser &: boolean \\
					-- upvotes &: int 
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getters & ... \\
					+ setters & ...
				\end{tabular}
			}
			
			\umlclass[left=5cm of Review]{Admin}{
				\begin{tabular}{@{} l l @{}}
					-- id & : Integer \\
					-- email & : String  
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getter & ... \\
					+ setter & ...
				\end{tabular}
			}
			
			\umlclass[below=1cm of Admin]{User}{
				\begin{tabular}{@{} l l @{}}
					-- hash & : String \\
					-- banned & : Boolean  
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getter & ... \\
					+ setter & ...
				\end{tabular}
			}
			
			\umlclass[below=1cm of User]{Report}{
				\begin{tabular}{@{} l l @{}}
					-- id & : Integer \\
					-- comment & : String \\
					-- date & : LocalDate \\
					-- issuerHash & : String \\
					-- reviewId & : int   
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getter & ... \\
					+ setter & ...
				\end{tabular}
			}
			
			\umlclass[below=1cm of Report]{PinChallenge}{
				\begin{tabular}{@{} l l @{}}
					-- id & : Integer \\
					-- pin & : String \\
					-- userHash & : String \\
					-- expiresAt & : Instant \\
					-- admin & : boolean   
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getter & ... \\
					+ setter & ...
				\end{tabular}
			}
			
			\umlclass[below=1cm of PinChallenge, type=record]{Token}{
				\begin{tabular}{@{} l l @{}}
					-- userHash & : String \\
					-- expiresAt & : long \\
					-- isAdmin & : boolean   
				\end{tabular}
			}{}
			
			\umlclass[right=5cm of Review]{School}{
				\begin{tabular}{@{} l l @{}}
					-- id & : Integer \\
					-- name & : String 
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getter & ... \\
					+ setter & ...
				\end{tabular}
			}
			
			\umlclass[below=1cm of School]{Degree}{
				\begin{tabular}{@{} l l @{}}
					-- id & : Integer \\
					-- name & : String \\
					-- type & : Type \\
					-- schoolId & : int 
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getter & ... \\
					+ setter & ...
				\end{tabular}
			}
			
			\umlclass[below=1cm of Degree]{Course}{
				\begin{tabular}{@{} l l @{}}
					-- id & : Integer \\
					-- name & : String \\
					-- degreeId & : int 
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getter & ... \\
					+ setter & ...
				\end{tabular}
			}
			
			\umlclass[below=1cm of Course]{Professor}{
				\begin{tabular}{@{} l l @{}}
					-- id & : Integer \\
					-- name & : String \\
					-- surname & : String 
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getter & ... \\
					+ setter & ...
				\end{tabular}
			}
			
			\umlclass[below=1cm of Professor]{Teaching}{
				\begin{tabular}{@{} l l @{}}
					-- id & : Integer \\
					-- profId & : Integer \\
					-- courseId & : Integer 
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getter & ... \\
					+ setter & ...
				\end{tabular}
			}
			
			\begin{umlpackage}[x=8, y=-14]{response}
				\umlclass[type=record]{ApiError}{
					-- error : String
				}{}
				\umlclass[type=record, right=1cm of ApiError]{ApiObjectCreated}{
					\begin{tabular}{@{} l l @{}}
						-- message & : string \\
						-- id & : int 
					\end{tabular}
				}{}
				\umlclass[type=record, below=1cm of ApiError]{ApiOk}{
					-- message : String
				}{}
			\end{umlpackage}
			
		\end{umlpackage}
		
		\umlinherit[geometry=|-|, anchor1=north, anchor2 = south]{DraftedReview}{Review}
		\umlinherit[geometry=|-|, anchor1=north, anchor2 = south]{PublishedReview}{Review}
	\end{tikzpicture}
	\caption{UML class diagram of the domain model.}
	\label{UML-domain-model}
\end{figure}

\paragraph{\textbf{Resemblance with the ER model.}} The classes are designed to align closely with their database counterparts, simplifying DB queries. To maintain this alignment, composition (nested objects) is intentionally avoided; instead, objects reference each other using internal database IDs. This flat structure is reflected in the simplicity of the domain model's UML diagram. (Figure \ref{UML-domain-model}).

\paragraph{\textbf{Review class inheritance.}} The \texttt{Review} class is the core entity of the project. Given its dual nature within EduMeter, it has been divided into two specialized subclasses. The parent class is implemented as an abstract class; it is not intended for polymorphic use, but rather to provide a uniform structure for its children. \texttt{PublishedReview} and \texttt{DraftedReview} are the specific classes utilized by the resource managers.

\paragraph{\textbf{Response interface.}} The \texttt{response} sub-package was created to standardize the management of error messages, object creation confirmations, and system notifications. These records provide a consistent structure for resource manager responses. This allows the endpoints to select the appropriate message type for an HTTP request result, which is then easily translated by the JSON manager into a legible format.

\paragraph{\textbf{POJOs.}} Many project classes are implemented as POJOs (Plain Old Java Objects) to keep the code simple and easily interpretable by Jackson when deserializing parameters from HTTP requests. Consistency logic is implemented directly within the getters and setters of each class to ensure that field values remain valid.

\subsection{Business Logic}

This package is responsible for the heavy lifting of the backend's functional duties. The logic has been divided into three distinct components, each providing a fundamental service to the entire project: \textbf{authentication service}, \textbf{resource endpoints} and \textbf{exception handlers}. These three packages actively engage with each other and with the ORM, which will be explored in section \ref{ORM-section}.

\subsubsection{Authentication and Authorization Service}
In EduMeter, users and admins needs to authenticate in order to perform their specific actions (publication and management). The authentication and authorization system is designed as a stateless, token-based security layer integrated into the JAX-RS request lifecycle. This design ensures secure communication and fine access control. Follows a description of all the structural decisions made by the team to implement this service. A detailed UML package diagram is also provided in Figure \ref{UML-auth}.

\paragraph{Declarative Security and Name Binding.} To secure REST endpoints, the system utilizes a declarative approach through custom annotations, making the code lighter and less repetitive, avoiding boiler plate control sequences. We have created 2 annotations:
\begin{itemize}
	\item \textbf{@AuthGuard}: applied to resources requiring standard user authentication (e.g up-voting reviews and creating reviews).
	\item \textbf{@AdminGuard}: applied to resources restricted to moderators (e.g. draft review and validation, report solving and behavioral countermeasures).
\end{itemize}

\noindent Both annotations utilize the \texttt{@NameBinding} meta-annotation, allowing JAX-RS to associate specific filters with annotated resource methods.

\paragraph{Request Filtering and Context Injection.} The security workflow is managed by two primary providers that intercept incoming traffic:
\begin{itemize}
	\item \textbf{AuthFilter}: This component intercepts requests marked with \texttt{@AuthGuard}. It extracts the \texttt{Bearer} token (a digital "entry pass" that identifies a user and their permissions automatically, allowing the system to verify them without needing to check a database every time) from the \texttt{Authorization} header and initiates validation through the \texttt{CryptoService}. Upon successful verification, it injects a custom \texttt{SecurityContext} into the request, establishing the user principal and defining roles such as \texttt{ADMIN} and \texttt{BASE}.
	\item \textbf{AdminFilter}: This filter extends \texttt{AuthFilter} to handle \texttt{@AdminGuard} requirements. It first executes the base authentication logic via \texttt{super.filter()} and then performs a secondary check to ensure the authenticated principal possesses the \texttt{ADMIN} role. Failure to meet this requirement results in a \texttt{ForbiddenException} (HTTP 403).
\end{itemize}

\paragraph{The Cryptographic Engine (CryptoService).}
The \texttt{CryptoService} serves as a singleton utility responsible for the platform's cryptographic operations.
\begin{itemize}
	\item \textbf{JWT Custom Design}: The service implements a simplified version of the JSON Web Token (JWT) concept. To reduce overhead, the standard JWT header is omitted, resulting in a two-part token (instead of three-part) consisting of a Base64-encoded JSON payload and an HMAC-SHA256 signature.
	\item \textbf{Signature Verification}: Tokens are signed using the \texttt{HmacSHA256} algorithm and a server-side secret. Validation uses \texttt{MessageDigest.isEqual} to compare signatures, providing protection against timing attacks.
	\item \textbf{User Anonymization}: One of the core EduMeter's features is complete user anonymity. User's sensitive information are never visible to other users nor admins and are never stored directly into the DB. To protect privacy while maintaining database efficiency, the service generates a \texttt{userHash}. This is achieved by computing a 16-byte truncated version of an HMAC-SHA256 hash of the user's email, resulting in a unique 22-character Base64 identifier.
\end{itemize}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[scale=0.7, transform shape]
		\umlclass[type= Jakarta interface, x=10, y=3]{ContainerRequestFilter}{}{}
		
		\begin{umlpackage}[y=-2]{auth}
			\begin{umlpackage}{annotations}
				\umlclass[type=@interface]{AuthGuard}{}{}
				\umlclass[right=2cm of AuthGuard, type=@interface]{AdminGuard}{}{}
			\end{umlpackage}
			
			\begin{umlpackage}[x=13, y=0]{filters}
				\umlclass{AuthFilter}{}{
					+ filter(...) : void
				}
				\umlclass[right=2cm of AuthFilter]{AdminFilter}{}{
					+ filter(...) : void
				}
			\end{umlpackage}
			
			\umlclass[x=12, y=-6, type = Singleton]{CryptoService}{
				\begin{tabular}{@{} l l @{}}
					-- static final TOKEN\_EXPIRE\_MINUTES & : long \\
					-- static final HMAC\_ALGO & : String           \\
					-- static instance & : CryptoSerice             \\
					-- final jsonMapper & : ObjectMapper            \\
					-- final mac & : Mac                            \\
					-- final revokedTokens & : Set<String>
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					-- CryptoService() & : CryptoService            \\
					+ static sync getInstance() & : CryptoService   \\
					+ generateToken(String, boolean) & : String     \\
					+ decodeToken(String) & : Token                 \\
					+ revokeToken(String) & : void                  \\
					+ getUserId(String) & : String                  \\
					\textasciitilde\ setClock(Clock) & : void
				\end{tabular}         
			}
			
			\umlclass[x=2, y=-6,type=record]{Token}{
				\begin{tabular}{@{} l l @{}}
					+ userHash & : String \\
					+ expiresAt & : long \\
					+ isAdmin & : boolean 
				\end{tabular}
			}{}
		\end{umlpackage}
		
		\umlinherit[anchor1=west, anchor2=east]{AdminFilter}{AuthFilter}
		\umldep[anchor1=west, anchor2=east, stereo=use]{CryptoService}{Token}
		\umlimpl[geometry=-|]{AuthFilter}{ContainerRequestFilter}
	\end{tikzpicture}
	\caption{UML class diagram of the authentication package.}
	\label{UML-auth}
\end{figure}

\paragraph{Token Lifecycle and Security Constraints.} Tokens are generated with a strict 30-minute validity window, ensuring a standard expiration date for every user login code. The revocation of such tokens is managed through a set of strings called \texttt{revokedTokens}, which is maintained to handle logout events or compromised tokens. While currently implemented using a \texttt{ConcurrentHashMap}, the service is designed for future migration to a Redis-based key store for persistent, distributed revocation management. The system requires a \texttt{SECRET} environment variable; if missing, it falls back to a randomly generated secure secret, ensuring that keys are invalidated upon every deployment for security.

\subsubsection{Resource endpoints} 

Resource endpoints are responsible for HTTP request dispatching and resolution. This encompasses multiple tasks, including authentication management, exception handling, and database interaction for records management. This layer represents the core of the backend, it glues the system components together and serves as the primary interface for client interaction.

\paragraph{\textbf{Single Responsibility Principle.}} The endpoints architecture has been designed to respect the single responsibility principle. Consequently, each endpoint is dedicated to managing only its specific resource, providing the necessary paths for user communication. As a representative example, in Listing \ref{userEndpointCode}, this approach is visible through the \texttt{UserEndpoint} class.  Each endpoint is injected with only its corresponding Resource DAO, which serves as its sole point of data access. It is also clearly noticeable in Figure \ref{UML-endpoints}, where classes do not interact with each other. \\

In a couple of cases this principle is crossed. This occurs in those endpoints serving, due to their nature, as multiple resources aggregators. For instance:

\begin{itemize}
	\item \texttt{reportEndpoints:} reports has been designed to be strictly related to a certain published review, hence, this class requires access both to the reports and the published review DAOs. Actively deleting justified reported reviews. The code is visible at the Listing \ref{reportEndpointCode}. 
	\item \texttt{courseEndpoints:} the endpoint have full access to the course resource and to the teaching resource. This is crucial in order to pair courses and professors accordingly. These are the single endpoints able to interact with the teaching resource. 
	\item \texttt{professorEndpoints:} differently from the previous one, these endpoints leverage the teaching resource access only with displaying intent. Therefore it is not a proper transgression of the SRP. Code visible in the Listing \ref{professorEndpointCode}. 
\end{itemize}

TODO: se si aggiunge dettagli sulla spiegazione di JAX-RS magari alleggerire qui
\paragraph{\textbf{Class structure.}} Each class defines a collection of endpoints all starting from a common root(e.g., \texttt{/user} in this example). The narrower endpoints characterize actions that user can perform on that path through an HTTP request. Different methods are annotated with different permission levels, some actions can be performed only by authenticated user or authenticated admins. This is perfectly visible on top of the method signature, along with all the other specific annotations enabling data emission or insertion. Every method concludes by returning a structured message to the client.

\begin{lstlisting}[language=Java, caption=Fragment of Report endpoint class, label=reportEndpointCode]
	
	@Path("/report")
	public class ReportEndpoints {
		private final ReportDAO reportDAO;
		private final PublishedReviewDAO reviewDAO;
		
		@Inject
		public ReportEndpoints(ReportDAO reportDAO, PublishedReviewDAO reviewDAO) {
			this.reportDAO = reportDAO;
			this.reviewDAO = reviewDAO;
		}
		
		...
		
		@POST
		@Consumes(MediaType.APPLICATION_JSON)
		@Produces(MediaType.APPLICATION_JSON)
		@AuthGuard
		public ApiObjectCreated create(@Context SecurityContext securityContext,
		Report report) {
			String userHash = securityContext.getUserPrincipal().getName();
			report.setIssuerHash(userHash);
			
			int id = reportDAO.add(report);
			
			return new ApiObjectCreated(id, "Report created");
		}

		...
		
		@POST
		@Path("/{report_id}/approve")
		@Produces(MediaType.APPLICATION_JSON)
		@AdminGuard
		public ApiOk acceptReport(@PathParam("report_id") int reportId) {
			Report r = this.get(reportId);
			this.delete(reportId);
			
			reviewDAO.delete(r.getReviewId());
			
			return new ApiOk("Report approved");
		}
	}
	
\end{lstlisting}

\begin{lstlisting}[language=Java, caption=Fragment of Professor endpoint class, label=professorEndpointCode]
	@Path("/prof")
	public class ProfessorEndpoints {
		private final ProfDAO profDAO;
		private final TeachingDAO teachingDAO;
		
		@Inject
		public ProfessorEndpoints(ProfDAO profDAO, TeachingDAO teachingDAO) {
			this.profDAO = profDAO;
			this.teachingDAO = teachingDAO;
		}
		
		@GET
		@Produces(MediaType.APPLICATION_JSON)
		public List<Professor> search(@QueryParam("query") String query,
		@QueryParam("course_id") Integer id) {
			return profDAO.search(query, id);
		}
		
		...
		
		@GET
		@Path("/{prof_id}/teaching")
		@Produces
		public List<Teaching> listTeachings(@PathParam("prof_id") int profId) {
			return teachingDAO.getByProf(profId);
		}
	}
	
\end{lstlisting}

\begin{lstlisting}[language=Java, caption=User endpoint class, label=userEndpointCode]
	@Path("/user")
	public class UserEndpoint {
		private final UserDAO userDAO;
		@Inject
		public UserEndpoint(UserDAO userDAO) {
			this.userDAO = userDAO;
		}
		
		@GET
		@Produces(MediaType.APPLICATION_JSON)
		@AdminGuard
		public List<User> search(@QueryParam("banned") Boolean banned) {
			return userDAO.search(banned);
		}
		
		@POST
		@Path("/{user_hash}/ban")
		@Produces(MediaType.APPLICATION_JSON)
		@AdminGuard
		public ApiOk ban(@PathParam("user_hash") String userHash) {
			User u = userDAO.get(userHash)
			.orElseThrow(() -> new NotFoundException("User not found"));
			u.setBanned(true);
			
			userDAO.update(u);
			
			return new ApiOk("User banned");
		}
		
	}
\end{lstlisting}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[scale=0.6, transform shape]
		\begin{umlpackage}{endpoints}
			\umlclass{AdminEndpoint}{
				- adminDAO : AdminDAO \\
			}{
			    \begin{tabular}{@{} l l @{}}
			    	+ getAll() & : List<Admin> \\
			    	+ get(int) & : Admin \\
			    	+ create(Admin) & : ApiObjectCreated \\
			    	+ delete(int) & : ApiOK 
			    \end{tabular}
				
			}
			
			\umlclass[right=0.7cm of AdminEndpoint]{UserEndpoint}{
				+ userDAO : UserDAO \\
			}{
				\begin{tabular}{@{} l l @{}}
					+ search(Boolean) & : List<User> \\
					+ getByHash(SecurityContext) & : User \\
					+ ban(String) & : Boolean \\
				\end{tabular}
			}
			
			\umlclass[right=0.7cm of UserEndpoint]{AuthEndpoint}{
				\begin{tabular}{@{} l l @{}}
					+ \underline{WHITELISTED\_DOMAINS} & : String \\
					+ \underline{PIN\_EXPIRATION\_MIN} & : int \\
					-- pinDAO & : PinDAO \\
					-- adminDAO & : AdminDAO \\
					-- record SendPinBody(String) & \\
					-- record LoginBody(String, String) & \\
					-- record LoginResponse(String) & 
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ sendPin(boolean, SendPinBody) & : ApiOK \\
					+ login(boolean, LoginBody) & : LogicResponse \\
					+ logout(String) & : ApiOK
				\end{tabular}
			}
			
			\umlclass[x=4, y=-12]{ReportEndpoint}{
				\begin{tabular}{@{} l l @{}}
					-- reportDAO & : ReportDAO \\
					-- userDAO & : UserDAO
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ getAll() & : List<Report> \\
					+ get(int) & : Report \\
					+ create(SecurityContext, Report) & : CreateResponse \\
					+ acceptReport(int,Boolean) & : void
				\end{tabular}
			}
			
			\umlclass[x=0.5, y=-6]{DegreeEndpoint}{
				-- degreeDAO : DegreeDAO
			}{
				\begin{tabular}{@{} l l @{}}
					+ search(String, Integer) & : List<Degree> \\
					+ get(int) & : Degree \\
					+ create(Degree) & : CreateResponse \\
					+ delete(int) & : ApiOK \\
					+ update(Degree) & : ApiOK
				\end{tabular}
			}
			
			\umlclass[right=0.5cm of DegreeEndpoint,y=-3]{SchoolEndpoint}{
				-- schoolDAO : SchoolDAO
			}{
				\begin{tabular}{@{} l l @{}}
					+ search(String) & : List<School> \\
					+ get(int) & : School \\
					+ create(School) & : CreateResponse \\
					+ delete(int) & : ApiOK \\
					+ update(School) & : ApiOK
				\end{tabular}
			}
			
			\umlclass[right=0.5cm of SchoolEndpoint, y=-3]{CourseEndpoint}{
				-- courselDAO : courseDAO
			}{
				\begin{tabular}{@{} l l @{}}
					+ search(String, Integer, Integer) & : List<Course> \\
					+ get(int) & : Course \\
					+ create(Course) & : CreateResponse \\
					+ delete(int) & : ApiOK \\
					+ update(Course) & : ApiOK
				\end{tabular}
			}
			
			\umlclass[right=2cm of ReportEndpoint]{ProfessorEndpoint}{
				\begin{tabular}{@{} l l @{}}
					-- profDAO & : ProfDAO \\
					-- teachingDAO & : TeachingDAO
				\end{tabular}
			}{
				\begin{tabular}{@{} l l @{}}
					+ search(String, Integer) & : List<Professor> \\
					+ get(int) & : Professor \\
					+ create(Professor) & : ApiObjectCreated \\
					+ delete(int) & : ApiOk \\
					+ update(Professor) & : ApiOk \\
					+ listTeachings(int) & : List<Teaching>
				\end{tabular}
			}
			
			\umlclass[x=3,y=-18]{PublishedReviewEndpoint}{
				+ publishedReviewDAO : PublishedReviewDAO
			}{
				\begin{tabular}{@{} l l @{}}
					+ search(Integer, ..., Integer, ContainerRequestContext) & : List<T> \\
					+ get(int, ContainerRequestContext) & : PublishedReview \\
					+ publish(PublishedReview, SecurityContext) & : ApiObjectCreated \\
					+ toggleVote(int, ContainerRequestContext) & : ApiOk \\
					+ delete(int, ContainerRequestContext) & : ApiOk \\
					+ update(PublishedReview, ContainerRequestContext) & : ApiOk \\
				\end{tabular}
			}
			
			\umlclass[right=2cm of PublishedReviewEndpoint,y=-6]{DraftReviewEndpoint}{
				-- reviewDAO : DraftReviewDAO
			}{
				\begin{tabular}{@{} l l @{}}
					+ getAll() & : List<DraftReview> \\
					+ get(int) &  : DraftReview \\
					+ publish(DraftReview, SecurityContext) & : ApiObjectCreated \\
					+ delete(int) & : ApiOk
				\end{tabular}
			}
			
		\end{umlpackage}
	\end{tikzpicture}
	\caption{UML class diagram of the endpoints package.}
	\label{UML-endpoints}
\end{figure}

\subsubsection{Exception Handlers} The \textbf{Exception Handlers} package is a fundamental component of the \textit{EduMeter} architecture, responsible for ensuring system robustness and providing a consistent interface for error reporting.

\paragraph{\textbf{Standardized Error Reporting.}} To prevent the leakage of sensitive internal state and to provide a predictable API for client-side consumption, this package intercepts all application-level exceptions and translates them into a standardized JSON format: \texttt{\{"error":"description of the issue"\}}. This mechanism ensures that the backend never returns default HTML error pages.

\paragraph{\textbf{Specialized Exception Mappers.}} The package utilizes the Jakarta \texttt{ExceptionMapper} interface to provide in-depth control over different error scenarios:

\begin{itemize}
	\item \textbf{Global Exception Handler}: Acts as a universal safety net for any \texttt{Throwable} not caught by more specific mappers. It preserves the HTTP status codes for \texttt{WebApplicationExceptions} while mapping all other unforeseen errors to HTTP 500 (Internal Server Error).
	\item \textbf{JSON Validation Mappers}: Specialized mappers such as \texttt{JsonParseExceptionHandler} and \texttt{UnrecognizedPropertyExceptionHandler} handle errors related to request payloads. These mappers return HTTP 400 (Bad Request), providing specific feedback when a client sends malformed JSON or invalid data fields.
\end{itemize}

The exception handling in JAX-RS operates through a hierarchical discovery process that prioritizes the most specific match available to resolve a failure. When an error occurs, the runtime builds a map of all classes annotated with \texttt{@Provider} and searches for an ExceptionMapper that matches the thrown exception type, starting from the most narrow "leaf" class and moving up the inheritance tree toward more general types.

In the \textit{EduMeter} implementation, it was mandatory to implement specific handlers for JSON exceptions, as there are already some implementations of those in the Jackson library, that would come up as more specific during the lookup, and our global handler wouldn't be called.

\vspace{2em}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[scale=0.8, transform shape]
		
		\umlclass[x=-4, y=6]{ExceptionMapper<Throwable>}{}{}
		\umlclass[x=5, y=6]{ExceptionMapper<InvalidFormat>}{}{}
		
		\umlclass[x=-4, y=-5]{ExceptionMapper<JsonParseException>}{}{}
		\umlclass[x=6, y=-5]{ExceptionMapper<UnrecognizedPropertyException>}{}{}
		
		\begin{umlpackage}[x=0.5, y=-8]{exceptionHandlers}
			
			\umlclass[x=-4.5, y=10]{ExceptionHandler}
			{}
			{+ toResponse(Throwable) : Response}
			
			\umlclass[x=4.5, y=10]{InvalidFormatExceptionHandler}
			{}
			{+ toResponse(Throwable) : Response}
			
			\umlclass[x=-4.5, y=7]{JsonParseExceptionHandler}
			{}
			{+ toResponse(Throwable) : Response}
			
			\umlclass[x=4.5, y=7]{UnrecognizedPropertyExceptionHandler}
			{}
			{+ toResponse(Throwable) : Response}
			
			\umlinherit[geometry=|-|, anchor1=30, anchor2=-50]{ExceptionHandler}{ExceptionMapper<Throwable>}
			\umlinherit{InvalidFormatExceptionHandler}{ExceptionMapper<InvalidFormat>}
			\umlinherit{JsonParseExceptionHandler}{ExceptionMapper<JsonParseException>}
			\umlinherit[geometry=|-|]{UnrecognizedPropertyExceptionHandler}{ExceptionMapper<UnrecognizedPropertyException>}
			
		\end{umlpackage}
		
	\end{tikzpicture}
	\label{UML-exceptin-handling}
	\caption{UML class diagram of the exception handling package.}
\end{figure}

%\paragraph{\textbf{Approach Advantages.}} Implementing multiple specialized mappers instead of a single general safety net provides several engineering advantages:
%\begin{itemize}
%	\item \textbf{Precise Client Feedback}: Clients receive exact details about validation errors (such as the specific unrecognized field name) rather than a vague "Internal Error".
%	\item \textbf{Semantic HTTP Accuracy}: This approach ensures that client-side mistakes correctly return HTTP 400 (Bad Request) codes, whereas a single safety net might incorrectly categorize them as 500 (Internal Server Error).
%	\item \textbf{Security and Sanitization}: Specific mappers allow for "sanitizing" error messages to ensure that internal database structures or logic are not leaked, while the general handler prevents the exposure of raw stack traces.
%	\item \textbf{Operational Efficiency}: Decoupling error handling from business logic allows core services to focus on the "happy path," while the provider architecture automatically manages the complexity of error translation at the edge of the application.
%\end{itemize}

\subsection{Object-Relation Mapper (ORM)} \label{ORM-section}
The Object-Relation Mapper (ORM) package has the responsibility of connecting the object-oriented domain model used within the business logic layer to the underlying data storage mechanisms. 

The application is designed to support two distinct storage backends: a volatile In-Memory storage (ideal for testing and rapid prototyping) and a persistent PostgreSQL remote database (intended for production environments). The selection of the active storage mechanism is determined dynamically at application startup by checking the \texttt{IN\_MEM\_DB} environment variable.

%\umlclass[x=15, y=-10]{DatabaseManager}{
%	\begin{tabular}{@{} l l @{}}
%		- instance & : DatabaseManager \\
%		- connection & : Connection
%	\end{tabular}
%}{
%	\begin{tabular}{@{} l l @{}}
%		- DatabaseManager() & : DatabaseManager \\
%		+ getInstance() & : DatabaseManager\\
%		+ getConnection() & : Connection \\
%
%	\end{tabular}
%}
\subsubsection{DAO Interfaces}
To achieve a strict separation between the data access logic and the core business layer, the ORM package uses the Data Access Object (DAO) design pattern alongside the Abstract Factory pattern. 

\paragraph{DAO pattern.}
The DAO pattern introduces a crucial abstraction layer for database interactions, effectively decoupling the application’s business logic from its persistence layer. It allows the business logic to interact with the database through simplified, high-level interfaces with standardised methods for all necessary CRUD operations. This hides the underlying complexities of data persistence such as query execution and connection management.

\paragraph{Abstract Factory pattern.}
The \texttt{DAOFactory} interface acts as the central Abstract Factory, establishing a contract for creating domain-specific DAOs. This allows the system to swap out the entire persistence implementation seamlessly. Currently, the application provides two concrete factory implementations:
	the \textbf{\texttt{InMemDAOFactory}} (produces DAOs that store data in volatile memory) and the
 \textbf{\texttt{PostgreDAOFactory}:} (produces DAOs that interact with a persistent PostgreSQL database).

During the startup phase, the \texttt{MainApplication} class uses a lambda-based \texttt{AbstractBinder} to dynamically configure the system based on the \texttt{IN\_MEM\_DB} environment variable: if it is present, it instantiates the \texttt{InMemDAOFactory}, otherwise it defaults to the \texttt{PostgreDAOFactory}. Using the selected factory instance, it binds the specific DAO interfaces (e.g., \texttt{UserDAO.class}) to their concrete implementations.

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[scale=0.7, transform shape]
		\begin{umlpackage}[minimum height=10.5cm]{orm}
			\begin{umlpackage}{dao}
				\umlclass[type=interface]{DAOFactory}{}{
					\begin{tabular}{@{} l l @{}}
						... & ... \\
						+ getDegreeDAO() & : DegreeDAO \\
						... & ...
					\end{tabular}
				}
				\umlclass[type=interface, right=3.5cm of DAOFactory]{AdminDAO}{}{
					\begin{tabular}{@{} l l @{}}
						+ get(int) & : Optional<Admin> \\
						+ getByEmail(String) & : Optional<Admin> \\
						+ getAll() & : List<Admin> \\
						+ delete(int) & : void \\
						+ add(Admin) & : int
					\end{tabular}
				}
			\end{umlpackage}

			\begin{umlpackage}{in-mem-dao}
				\umlclass[x=7.5, y=-5]{InMemAdminDAO}{}{}

				\umlclass[type=interface, x=7.5, y=-8]{InMemDAOFactory}{}{}
			\end{umlpackage}

			\begin{umlpackage}{postgre-dao}
				\umlclass[right=2.16cm of InMemAdminDAO]{PostgreAdminDAO}{}{}
				\umlclass[type=interface, right=2cm of InMemDAOFactory]{PostgreDAOFactory}{}{}
			\end{umlpackage}
			
		\end{umlpackage}
		
		\umldep[geometry=|-|]{InMemDAOFactory}{InMemAdminDAO}
		\umldep[geometry=|-|]{PostgreDAOFactory}{PostgreAdminDAO}
		\umldep[anchor1=east, anchor2=west]{DAOFactory}{AdminDAO}
		
		\umlinherit[geometry=-|, arm1=1, anchor1=-5]{InMemAdminDAO}{AdminDAO}
		\umlinherit[geometry=-|, arm1=1, anchor1=185]{PostgreAdminDAO}{AdminDAO}
		
		\umlinherit[geometry=|-|,anchor1=south, arm1=-1]{InMemDAOFactory}{DAOFactory}
		\umlinherit[geometry=|-|, anchor1=south, arm1=-1]{PostgreDAOFactory}{DAOFactory}
	\end{tikzpicture}
	\caption{Partial UML class diagram of the ORM package. This diagram display only the portion related to the Admin resource, the part referred to the other resources have the exact layout, therefore, it is omitted.}
	\label{UML-ORM}
\end{figure}

\subsubsection{In Memory Storage}
The In-Memory implementation provides a lightweight, volatile storage solution perfectly suited for rapid prototyping, unit testing, and development environments where the overhead of a persistent database connection is unnecessary. All classes for this implementation reside within the \texttt{in\_mem\_dao} sub-package.

Each class directly implements its respective domain interface and manages its own internal state entirely within the JVM heap. Key characteristics of this implementation include:

\begin{itemize}
	\item \textbf{Data structures as tables:} The core of the in-memory storage relies on standard Java Collections rather than external tables. Each DAO utilizes a \texttt{Map<Integer, T>} to simulate a relational database table where the \texttt{Integer} key acts as the unique primary key, while the map's value holds the corresponding domain object instance.
	\item \textbf{Auto-incrementing IDs:} To mimic the behavior of a relational database sequence (like \texttt{SERIAL} in PostgreSQL), each DAO maintains a local integer counter. During an \texttt{add} operation, the domain object is assigned the current ID before being inserted into the \texttt{store} map, and the counter is subsequently incremented.
	\item \textbf{Query Simulation via Streams API:} Basic CRUD operations are implemented with native Map methods like \texttt{store.get(id)} and \texttt{store.remove(id)}. For queries that require filtering by non-key attributes (such as \texttt{getByEmail}), the DAOs leverage the Java Streams API. They iterate over the Map's values, apply the necessary filter predicates, and return the matching elements (e.g., \texttt{store.values().stream().filter(...).findAny()}).
	\item \textbf{Inter-DAO Relationships:} To manage complex queries and simulate relational joins, the DAO can maintain references to other DAO instances, that are passed through the constructor, to fetch the related objects it needs to complete the query.
\end{itemize}

\subsubsection{Postgre Remote Storage}
The PostgreSQL implementation provides a persistent storage solution intended for production environments. This sub-package utilizes a layered inheritance structure to minimize boilerplate code and ensure consistent database interaction patterns across all resources.

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[scale=0.7, transform shape]
		\begin{umlpackage}{orm}
			\begin{umlpackage}{postgre-dao}
				\umlclass[type=abstract]{PostgreDAO}{}{
					\begin{tabular}{@{} l l @{}}
						- setParams(PreparedStatement, List<Object>) & : void \\
						\# \textit{mapRowToObject(ResultSet)} & : T \\
						\# rawQuery(String, List<Object>) & : ResultSet \\
						\# selectQuery(String, List<Object) & : List<T> \\
						\# insertquery(String, List<Object) & : int \\
						\# updateQuery(String, List<Object>) & : void \\
					\end{tabular}
				}
				
				\umlclass[below=1.5cm of PostgreDAO]{PostgreAdminDAO}{}{
					\begin{tabular}{@{} l l @{}}
						\# mapRowToObject(ResultSet) & : Admin \\
						+ get(int) & : Optional<Admin> \\
						+ getByEmail(String) & : Optional<Admin> \\
						+ getAll() & : List<Admin> \\
						+ delete(int) & : void \\
						+ add(Admin) & : int 
					\end{tabular}
				}
			\end{umlpackage}
			
			\begin{umlpackage}{dao}
				\umlclass[type=interface, left= 1.5cm of PostgreDAO]{AdminDAO}{}{
					\begin{tabular}{@{} l l @{}}
						+ get(int) & : Optional<Admin> \\
						+ getByEmail(String) & : Optional<Admin> \\
						+ getAll() & : List<Admin> \\
						+ delete(int) & : void \\
						+ add(Admin) & : int
					\end{tabular}
				}
			\end{umlpackage}
		\end{umlpackage}	
		
		\umlimpl[geometry=-|]{PostgreAdminDAO}{AdminDAO}
		\umlinherit{PostgreAdminDAO}{PostgreDAO}
	\end{tikzpicture}
	\caption{An example of a concrete PostgreDAO class (PostgreAdminDAO) and its relations to other classes.}
\end{figure}

\paragraph{The PostgreDAO Base Class.}
The core of the PostgreSQL implementation is the abstract \texttt{PostgreDAO<T>} class. Through the use of Java Generics and the JDBC API, it provides a template that heavily reduces boilerplate code across the data access layer. Key features of this base class include:

\begin{itemize}
	\item \textbf{Centralized queries management:} It encapsulates the repetitive mechanics of JDBC in protected wrapper methods like \texttt{selectQuery}, \texttt{insertQuery}, and \texttt{updateQuery}. They automatically handle connection retrieval, statement preparation, and the execution lifecycle, keeping concrete DAOs clean.
	\item \textbf{Secure query execution:} Having methods accept SQL queries as \texttt{String} parameters is completely safe in this architecture. Because these methods are \texttt{protected}, they are strictly intended to be called by concrete DAO subclasses using internally hardcoded SQL strings, not direct user input.
	\item \textbf{Abstract Result Mapping:} While the base class manages executing the query and iterating through the \texttt{ResultSet}, it delegates the actual object creation to its subclasses via the abstract \texttt{mapRowToObject} method.
\end{itemize}

\paragraph{Concrete DAOs.}
Concrete classes have the purpose of implementing the methods defined by their respective domain interfaces connecting them directly to the database. Their role focuses on \textbf{constructing the SQL query} based on the input parameters, delegating all the execution infrastructure to the base class.

\begin{itemize}
	\item \textbf{Construction of queries:} For basic operations creating a query translates to defining static SQL strings with placeholders (e.g., \texttt{WHERE email = ?}) paired with a simple \texttt{List<Object>} that stores the parameters. For more complex methods, the query is dynamically assembled using a \texttt{StringBuilder}; depending on the actual input parameters (e.g., whether \texttt{schoolId} or \texttt{degreeId} are provided or null), the concrete class decides which \texttt{JOIN} and \texttt{WHERE} clauses to append, concurrently populating the parameter list.
	\item \textbf{Execution delegation to PostgreDAO:} Once the query (as a string) and its parameters have been constructed they are passed to the protected methods of the \texttt{PostgreDAO} superclass.
	\item \textbf{Data Mapping:} Every class must implement the abstract \texttt{mapRowToObject} method by mapping the raw results (\texttt{ResultSet}) returned by the database into the correct domain objects (\texttt{Admin}, etc.).
\end{itemize}

\begin{lstlisting}[language=Java, caption=Example of a concrete PostgreDAO class, label=concretePostgreDAO]
	public class PostgreAdminDAO extends PostgreDAO<Admin> implements AdminDAO {
	
		@Override
		protected Admin mapRowToObject(ResultSet rs) throws SQLException {
			return new Admin(rs.getInt("id"), rs.getString("email"));
		}
		
		@Override
		public Optional<Admin> get(int id) {
			String query = "SELECT * FROM Admin WHERE id = ?";
			List<Object> params = List.of(id);
			
			return selectQuery(query, params).stream().findFirst();
		}
		
		... other merthods ...
	}
\end{lstlisting}


\subsection{Database}
When the remote storage option is selected, the application relies on a PostgreSQL database to ensure reliable and persistent data storage. This database must be instantiated on the host environment and properly configured to interact seamlessly with the application back-end.

\subsubsection{Connection}
The connection to the database is managed by a dedicated class: \texttt{DatabaseManager}. This class is structured using the Singleton design pattern to ensure that only a single instance manages database connectivity throughout the application's lifecycle. Access to this instance is controlled via a synchronized \texttt{getInstance()} method, ensuring thread safety even in concurrent environments.

To handle communication with the database, the class provides a \texttt{getConnection()} method. This method optimizes resource usage by first checking if an active connection already exists; if the connection is null or closed, it proceeds to establish a new one.
 
To establish the connection three variable must be set: 
\begin{itemize}
	\item \texttt{DB\_URL}: The connection string that tells the JDBC driver where your database is hosted and which specific database instance to connect to. It follows the format:\\ \texttt{jdbc:postgresql://host:port/database\_name}.
	\item \texttt{DB\_USER}: This is the username of the PostgreSQL account that can access, initialize, and modify the database.
	\item \texttt{DB\_PASSWORD}: The database password related to the user.
\end{itemize}
For security and deployment flexibility, credentials are never hardcoded; instead, they are memorized as environment variable and the \texttt{DatabaseManager} dynamically retrieves them when necessary. If any of these essential variables are missing, the system immediately halts the process by throwing an \texttt{IllegalStateException}. 

Once the environment variables are successfully validated, the manager loads the PostgreSQL JDBC driver (\texttt{org.postgresql.Driver}) and establishes the connection through the \texttt{DriverManager}.

\subsubsection{Structure}
\paragraph{Initialization.}
When the remote storage option is active and \texttt{PostgreDAOFactory} is instantiated, the database schema is automatically initialized. The factory's constructor triggers an \texttt{initDatabase()} method, which reads an \textit{init.sql} file located in the application's resources folder. The factory requests a connection from the \texttt{DatabaseManager} and executes the script as a single query string.

This automated setup process is inherently safe and idempotent. All queries within the \textit{init.sql} script utilize the \texttt{CREATE TABLE IF NOT EXISTS} clause, ensuring that existing data or structures are never accidentally overwritten if the database has already been configured. 

\paragraph{Implementation.}
The database has been structured following the relational Entity-Relationship schema in Figure \ref{ER model}. The architecture is built around several interconnected core entities:
\begin{itemize}
	\item \textbf{Users \& Authentication:} The \texttt{Users} table manages standard accounts (including ban status), while administrative access is handled by the \texttt{Admin} table. Authentication and password recovery rely on a \texttt{Pin} table, which stores temporary codes, their expiration timestamps, and the user's administrative status.
	\item \textbf{Academic Hierarchy:} The educational structure is represented by linking \texttt{School}, \texttt{Degree}, \texttt{Course}, and \textbf{Professor} tables. A central associative entity, \texttt{Teaching}, acts as a bridge to associate specific professors with specific courses.
	\item \textbf{Review System:} The core functionality revolves around the \texttt{Published Review} and \texttt{Drafted Review} tables. Published reviews are linked to a specific \texttt{Teaching} instance and a \texttt{User}, storing rating, difficulty, and text comments. Drafts contain similar, though less strictly constrained, information before final submission.
	\item \textbf{Interaction \& Moderation:} To support community features, an \texttt{Up Vote} table tracks which users have liked specific reviews. Additionally, a \texttt{Report} table allows users to flag problematic reviews, linking the report comment directly to the user and the review in question.
\end{itemize}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[scale=0.8, transform shape]
		\node[umlclass] (Users) {
			\textbf{Users}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id} 	& \textit{char} \\
							& banned 		& \textit{boolean}
			\end{tabular}
		};
		
		\node[umlclass, below = 1cm of Users] (PublishedReview) {
			\textbf{Published Review}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id} 	& \textit{int} \\
				\textbf{FK} & user\_id 		& \textit{int} \\
							& date			& \textit{date} \\
				\textbf{FK} & teaching\_id 	& \textit{int} \\
							& rating		& \textit{int} \\
							& difficulty  	& \textit{int} \\
							& comment 		& \textit{text} \\
			\end{tabular}
		};
		
		\node[umlclass, below = 1cm of PublishedReview] (Teaching) {
			\textbf{Teaching}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id}	& \textit{id} \\
				\textbf{FK} & course\_id 	& \textit{int} \\
				\textbf{FK} & professor\_id & \textit{int} \\
			\end{tabular}
		};
		
		\node[umlclass, above = 1cm of Users] (PinChallenge) {
			\textbf{Pin Challenge}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id} 	& \textit{int} \\
							& pin	 		& \textit{varchar} \\
				\textbf{FK} & user\_id 		&\textit{char} \\
							& expires\_at 	&\textit{timestamp} \\
							& is\_admin 	&\textit{boolean}
			\end{tabular}
		};
		
		\node[umlclass, left = 1.5cm of PublishedReview] (UpVote) {
			\textbf{Up Vote}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK FK} & \textbf{user\_id}   & \textit{char} \\
				\textbf{PK FK} & \textbf{review\_id} & \textit{int} \\
			\end{tabular}
		};
		
		\node[umlclass, above = 1cm of UpVote] (DraftedReview) {
			\textbf{Drafted Review}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id} 	& \textit{int} \\
				\textbf{FK} & user\_id 		& \textit{char} \\
							& date 			& \textit{date} \\
							& school 		& \textit{varchar} \\
							& degree 		& \textit{varchar} \\
							& course 		& \textit{varchar} \\
							& professor		& \textit{varchar} \\
							& rating 		& \textit{int} \\
							& difficulty 	& \textit{int} \\
							& comment		& \textit{varchar} \\
			\end{tabular}
		};
		
		\node[umlclass, above = 1cm of DraftedReview] (Admin) {
			\textbf{Admin}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id} 	& \textit{int} \\
							& email			& \textit{varchar} \\
			\end{tabular}
		};
		
		
		
		\node[umlclass, left = 1.5cm of Teaching] (Professor) {
			\textbf{Professor}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id} 	& \textit{int} \\
							& name 			& \textit{varchar} \\
							& surname		& \textit{varchar} \\
			\end{tabular}
		};
		
		\node[umlclass, right = 1.5cm of Teaching] (Course) {
			\textbf{Course}
			\nodepart{two}
			\begin{tabular}{ l l l}
				\textbf{PK} & \textbf{id} 	& \textit{int} \\
							& name 			& \textit{varchar} \\
				\textbf{FK} & degree\_id 	& \textit{int} \\
			\end{tabular}
		};
		
		\node[umlclass, above = 1cm of Course] (Degree) {
			\textbf{Degree}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id} 	& \textit{int} \\
							& name 			& \textit{varchar} \\
							& type 			& \textit{varchar} \\
				\textbf{FK} & school\_id 	& \textit{int} \\
			\end{tabular}
		};
		
		\node[umlclass, above = 1cm of Degree] (School) {
			\textbf{School}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id} 	& \textit{int} \\
							& name 			& \textit{varchar} \\
			\end{tabular}
		};
		
		\node[umlclass, above = 2cm of School] (Report) {
			\textbf{Report}
			\nodepart{two}
			\begin{tabular}{l l l}
				\textbf{PK} & \textbf{id} 	& \textit{int} \\
							& comment		& \textit{varchar} \\
							& date 			& \textit{date} \\
				\textbf{FK} & user\_id 		& \textit{char} \\
				\textbf{FK} & review\_id 	& \textit{int}
			\end{tabular}
		};
		
		\draw[umlarrow] (Report.west) -- ++(-0.5,0) |- (Users.east);
		\draw[umlarrow] (Report.west) -- ++(-0.5,0) |- (PublishedReview.east);
		\draw[umlarrow] ([yshift=-4mm]DraftedReview.east) --  ([yshift=4mm]Users.west);
		\draw[umlarrow] (PublishedReview) -- (Users);
		\draw[umlarrow] (Course) -- (Degree);
		\draw[umlarrow] (Degree) -- (School);
		\draw[umlarrow] (Teaching) -- (Course);
		\draw[umlarrow] (Teaching) -- (Professor);
		\draw[umlarrow] (PublishedReview) -- (Teaching);
		\draw[umlarrow] (PinChallenge) -- (Users);
		\draw[umlarrow] (UpVote.east) -- ++(0.55,0) |- ([yshift=-4mm]Users.west);
		\draw[umlarrow] (UpVote.east) -- (PublishedReview);
		
	\end{tikzpicture}
	\caption{UML diagram of Database schema.}
\end{figure}
\subsection{Interface}
