\section{Introduction}

At some point in their academic journey, every student faces the challenge of selecting their elective courses required for graduation. Choosing the right "free choice" exam is difficult for several key reasons:

\begin{itemize}
	
	\item \textbf{Informative gap}: a major hurdle is the lack of up-to-date and relevant information regarding course material, examination formats, and the actual workload involved. Without these details, making an informed decision is nearly impossible.
	
	\item \textbf{Community experience}: the opinions of former students are essential for determining if a course aligns with one's academic goals and timeline. Unfortunately, it is often difficult to locate peers on campus or in online chats who are available to provide honest and detailed answers about specific subjects.
	
	\item \textbf{Professor competence}: the quality of a course is largely determined by the professor's teaching ability and their availability to students. It is nearly impossible to gauge a professor’s effectiveness without attending their lectures; however, this information is needed at the start of the semester, not at the end, when study plans are already locked and time has run out.
	
\end{itemize}

\noindent The solutions to all these problems is \textbf{EduMeter}, a platform made for students by students. 

\subsection{Statement}

\textbf{EduMeter} is a dedicated web platform for bachelor’s and master’s students at the University of Florence. It serves as a central hub for viewing and publishing reviews of university courses, fostering a transparent academic community. \\

The system categorizes users into three distinct roles, each with specific permissions and capabilities:

\begin{itemize}

    \item \textbf{Guest User}: unauthenticated users can browse the entire collection of course reviews. To ensure ease of navigation, guests can apply various filters to search through review's metadata. This type of user is not able to write any review.
	
	\item \textbf{Student User}: once authenticated via a personal institutional email, students can browse the corpus and post new reviews. To encourage honest feedback, all student identities remain strictly anonymous within the platform. The community of students can choose to up-vote the best reviews and also report unfair behaviors to the Admin. 
	
    \item \textbf{Admin}: this administrative role is responsible for overseeing the platform's integrity. Admins verify the information submitted by students and hold full CRUD (Create, Read, Update, Delete) permissions to manage the system’s data records.
    Moreover, the Admin has the responsibility of managing student's report and, eventually, has the power to ban them. Every operation is performed on a separate control panel which the Admin can log into with his personal verified email.

\end{itemize} 

\vspace{.7em}
		
\begin{figure}[H]
	
	\centering
	\begin{tikzpicture}[thick, font=\sffamily]
		
		% 1. ADMIN Ellipse (Left - Green)
		\draw[fill=green!20, fill opacity=0.5] (0,0) ellipse (4cm and 1.3cm);
		\node[text=green!40!black] at (-2.5, 1.5) {\textbf{ADMIN}};
		
		% 2. USER Ellipse (Right - Blue)
		\draw[fill=blue!20, fill opacity=0.5] (3,0) ellipse (4cm and 1.3cm);
		\node[text=blue!70!black] at (5.5, 1.5) {\textbf{USER}};
		
		% 3. GUEST Label (Placed in the intersection)
		% The intersection center is roughly at (1.5, 0)
		\node[text=red!70!black] at (1.5, 0) {\textbf{GUEST}};
		
		% --- Example Permissions ---
		\node[scale=0.8] at (-2.5, 0) {Verify Reviews};
		\node[scale=0.8] at (5.5, 0) {Submit Reviews};
		\node[scale=0.8] at (1.5, -0.7) {View Reviews}; % Guest (Intersection)
		
	\end{tikzpicture}
	\caption{Permission overlap Venn Diagram with some examples of permitted actions per user category.}
	
\end{figure}

\noindent
To ensure consistency and data integrity, each review follows a standardized structure. Students must complete the following numerical and string fields to submit their feedback:

\begin{itemize}
	\item \textbf{Teaching}: A Course and Professor pair chosen from a predefined list. 
	If the desired teaching is not available, the reviewer can manually complete the following string fields:
	\begin{itemize}
		\item \textbf{Professor}: name and surname of the professor who held the course.
		\item \textbf{Course}: name of the evaluated course.
		\item \textbf{Degree}: the degree associated to the course.
		\item \textbf{School}: the school offering the degree.
	\end{itemize}
	\item \textbf{Difficulty}: numerical value representing the student's perceived course difficulty.
	\item \textbf{Enjoyment}: numerical value indicating the reviewer's overall course enjoyment.
	\item \textbf{Comment}: text field for providing detailed qualitative feedback.
\end{itemize}
Upon submission, reviews with a predefined teaching are published immediately. However, if the teaching was manually entered, an Admin must verify the provided data and add a new entry to the application database before the review becomes public.

\subsection{Review validation system: iterative design}

A major challenge during the system design of \textit{EduMeter} was conceptualizing the data collection process. The required dataset included courses, degree programs, schools, professors, and the specific relational mappings between courses and their respective instructors. \\

Through an iterative design process, we evaluated several methodologies before finalizing the community-based data acquisition and maintenance system detailed later in this report.

\subsubsection{Evaluated and Discarded Approaches}

During the initial phases, we explored three main ideas, which were ultimately discarded due to technical or administrative constraints:

\begin{itemize}[leftmargin=*]
	\item \textbf{Institutional System Integration:} our initial idea was to automate data retrieval directly from the university's centralized IT systems, potentially leveraging identity providers like SPID (replicating how the university grants students access to their portals). Accessing to all the student personal information upon authentication automatically. In this way the user could only post reviews about those courses he have actually completed.
	\begin{quote}
		\textit{Outcome:} Discarded. This approach presented severe privacy implications and required official university authorization, which was unfeasible to obtain.
	\end{quote}
	
	\item \textbf{Web Scraping:} we considered scraping the required data directly from the official Cineca database \href{https://unifi.coursecatalogue.cineca.it}{(link)}.
	\begin{quote}
		\textit{Outcome:} Discarded. After a preliminary analysis, building and maintaining web scrapers for this specific database proved to be too difficult and time consuming.
	\end{quote}
	
	\item \textbf{Static Hardcoding:} we briefly evaluated manually hardcoding all existing courses from the Cineca database into our system.
	\begin{quote}
		\textit{Outcome:} Discarded. This idea was immediately rejected due to the massive volume of courses and professors, making it completely unscalable.
	\end{quote}
\end{itemize}

\subsubsection{Final Solution: community-based data collection}

To ensure independence and maintainability, we ultimately adopted a fully autonomous, user-driven system. Students populate the database by manually inputting course details as they submit their reviews. 

To guarantee data integrity, the system utilizes a semi-automated validation process managed by administrators. The platform has two types of submitted data: \textbf{Verified Data}, if a user selects a course already present in the platform's internal database, the review is published automatically. \textbf{Unverified Data}, if a user inputs a \textit{new} course, the review enters a two-step publication pipeline where an administrator must verify that the submitted data officially exists before it is published.

Unlike the previously explored methods, this crowdsourced approach does not rely on any external data sources and is highly maintainable. However, the trade-off is the necessity of an administrator role to validate new entries and a slightly longer, two-step publication process for reviews on previously unrecorded courses.

\subsection{System architecture and tools}\label{system-architecture-section}

EduMeter is a web application divided into two distinct parts that rely on several industrial-grade libraries:

\paragraph{\textbf{Backend.}}
This part is responsible for managing the core application logic, interfacing with a PostgreSQL database and auxiliary servers for external services, such as SMTP. Developed in Java, it exposes a RESTful HTTP API. The codebase is organized into three primary packages to ensure modularity and separation of responsibilities:

\begin{itemize}
	\item \textbf{Business Logic}: Contains the application’s functional requirements, including \textbf{REST} endpoints, and \textbf{authentication management}.

		The \textbf{authentication} flow includes sending emails and issuing \textbf{JWT}s (JSON Web Tokens). Sending emails is not an implemented feature, as it would rely on an external service to handle SMTP transfers, but JWTs are correctly issude using \textbf{HMAC} algorithm, which is also used to compute unique and secure user hashes.

	\item \textbf{Domain Model}: Defines the system's core entities, such as: school, degree, course and user. Each class encapsulates specific invariants and behaviors that model real-world scenarios. 
	
	\item \textbf{DAO (Data Access Object)}: Abstracts the persistence layer from the business logic. This package includes an interface layer to provide an easy swap between DAOs implementations. \textbf{FIXME: sistema questa frase dalla virgola in poi}
	Additionally to the DAOs for the PostgreSQL DB, there's an implementation of an \textbf{in-memory storage system}, which provides a lightweight testing environment that remains independent of the production database.
\end{itemize}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[thick, font=\sffamily]

	\begin{umlpackage}{business-logic}
		\begin{umlpackage} {auth} \end{umlpackage}
		\begin{umlpackage}[x=3] {endpoints} \end{umlpackage}
		\begin{umlpackage}[x=2,y=-3] {exception-handlers} \end{umlpackage}
	\end{umlpackage}
	\begin{umlpackage}[x=3, y=-7, minimum width=3cm]{models}\end{umlpackage}
	\begin{umlpackage}[x=8]{orm}
		\begin{umlpackage} [x=0]{dao} \end{umlpackage}
		\begin{umlpackage}[x=4, y=-3] {postgre-dao} \end{umlpackage}
		\begin{umlpackage}[x=0, y=-3] {in-mem-dao} \end{umlpackage}
	\end{umlpackage}

	\umlimport[geometry=|-, anchor1=-130, anchor2=west]{business-logic}{models}
	\umlimport[geometry=-|-, anchor1=east, anchor2=west]{endpoints}{dao}
	\umlimport[geometry=|-, anchor1=-130, anchor2=east]{orm}{models}

	\umlimport[geometry=-|, anchor1=east, anchor2=30, arm1=5cm]{dao}{postgre-dao}
	\umlimport[geometry=-|, anchor1=east, anchor2=30]{dao}{in-mem-dao}

	% DB node
	\node[cylinder, 
		shape border rotate=90, 
		draw, 
		minimum height=2.5cm, 
		minimum width=2cm, 
		aspect=0.25, 
		fill=gray!10, 
		align=center] (db) at (12, -7) {PostgreSQL\\Database};

	\draw[<->, >=latex, line width=1pt] (db) -- (postgre-dao)
	node[left, midway] {JDBC};

	\end{tikzpicture}
	\caption{UML diagram of the complete code-base. Comprehensive of each component and relationship between each.}
	\label{UML-overall-diagram}
\end{figure}

\paragraph{\textbf{Frontend.}} This component represents the user-facing interface of the platform, specifically tailored for the student body. While the full implementation of the frontend was considered out of scope for the current phase of the project, a comprehensive set of mock-ups is provided in section \ref{mock-ups} to illustrate the intended final product. The interface design prioritizes a seamless UX; every element has been created to guide the user intuitively through the processes of browsing and publishing reviews. A dedicated control panel, accessible only to authenticated admins, provides the right functionalities in order to ease the work of moderating the community and managing the review corpus. 

\paragraph{\textbf{Libraries.}} The back-end has been built using these libraries in order to create an industrial-grade product easy to maintain and up-to-date with the most sophisticated technologies. Following a list of each framework used:

\begin{itemize}
	\item JAX-RS for REST API.
	\item JDBC for database connectivity.
	\item Glassfish for Jakarta EE open source implementation.
	\item Mockito for testing.
\end{itemize}

\noindent Developed using:

\begin{itemize}
	\item Intellij Idea as the main IDE.
	\item Insomnia as a REST testing client.
	\item AI models to automate boring repetitive coding.
	\item Apache Tomcat as the webserver.
\end{itemize}
\pagebreak